### 2014-03-08 src/analysis.Rnw
update

\begin{figure*}[t]
<<x.per.sel,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)
@
\label{fig:sel}
\end{figure*}[t]

>>>>

\begin{figure*}[t]
<<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)
@
\label{fig:sel}
\caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\end{figure*}[t]

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)
@
\label{fig:sel}
\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
\end{figure*}[t]
